% !TeX spellcheck = <none>

\section{{Data and Methodology}}



\subsection{{Data and Sample}}



Our data has several unique features which distiguishes our paper from the existing literature. Stock ownership data for Iranian public firms is available with daily frequncy reprted at the end of each trading day. This data includes all blockholders, defined as having at least one percent of the outstanding shares in a firm for all investor types- institutional as well as individuals- and is automatically reported by a central authority named Tehran Securities Exchange Technology Managament Corporation (TSETMC), which is a subsidiary of Tehran Stcok Exchange. This eliminates potential issues present in self-reported data (such as those exisiting in US institutional holding data, known as 13F filings). In order to put together our dataset, we compile daily stock ownerhip tables (available in a separate table for each firm) which are publicaly available starting from March 2010.


We also collect data on business groups, defined as groups of listed firms with interconnected ownership structures controlled by an ultimate owner. Business groups are common organizational structure in corporate ownership in Iran as well as many other parts of the world. Around three quarters of Iranian public firms are part of complex interlinked ownership networks each governed by an ultimate owner, which sits at the top of a multi-layer pyramid ownership structure ({\cite{Aliabadi2022}}). Unlike countries like South Korea, Japan, and India that formally announce business groups, we do not have officially defined business groups in Iran. We use data provided by {\cite{Aliabadi2022}} which builds a comprehensive data of all Iraninan business groups using the methodology introduced in \cite{almeida2011structure} with a 40\% threshold for control rights. \footnote{For further discussion see appendix \ref{BGDef}} This data covers March 2015 to March 2020. 



	We also gather stock returns, trading volume, firm-level trading data and accounting information from Codal (equvalent to SEC's EDGAR) \footnote{\href{http://www.codal.ir}{www.codal.ir}}
and TSETMC's website \footnote{\href{http://www.tsetmc.com}{www.tsetmc.com}}.

We exclude ETFs. 
We restrict our empirical analysis to 2015/03-2020/03 (1393/01-1398/12 Persian calendar) due to the availability of daily ownership data and the special events \footnote{
	The Tehran Stock Exchange's main index (TEPIX) raised exponentially to quadruple value and then fell sharply due to the gigantic entrance of new individual investors that seems to be a bubble period from that period.} that happened after 2020/03, which may affect our results. 



Panel \subref{t2-1} table \ref{st1} reports summary statistics of ownership data and business groups. As shown in the table, 494 firms on average have five block-holders that own 73 percent of them. There are 43 business groups on average, with seven members which own 314 (63\%) firms. 






\subsection{{Pair composition} }

	If two firms have at least one common block-holder, We consider them as a pair. By this definition, there are \input{Elements/pairsnumber}  unique pairs in entire periods, which is \input{Elements/PairPercent.tex}of possible pairs (\input{Elements/TotalPairNumberCal.tex}). As we expected, stocks in pairs have concentrated ownership relative to the total sample, and pairs have one common owner.
	
	\normalcolor
	
	As one of our empirical studies, we study the impact of being in the same business group relative to being in two distinct groups on pair's correlation. 
%	(Further explanations about business groups are in section \ref{BGDef} )
	For assigning one pair to a group, both firms should belong to one ultimate owner. Another possibility is that each firm belongs to a different ultimate owner or one of them, or both of them do not belong to any groups, which all of them illustrated in figure \ref{g2-1}.
	By classifying pairs, on average, \input{Elements/SameBGpercent.tex}of them  belong to one business group. We report summary statistics of ownership features for all pairs in panel \subref{t2-2} table \ref{st1}.
	
	\captionsetup[subfigure]{labelformat=parens,font=footnotesize}
			\renewcommand{\thesubfigure}{\Alph{subfigure}}	
	\begin{figure}[htbp]
		\centering
		\caption{ Three categories for pairs base on being in business groups}
		\label{g2-1}
		\normalcolor
		\begin{subfigure}[t]{1\linewidth}
			
			\resizebox{0.49\textwidth}{!}{
				\begin{tikzpicture}[node distance=2cm]
					
					
					
					\node (CH) [process,yshift = -2cm ,xshift=3.5cm] {Common Owner};
					
					\node (end) [startstop1,left of = CH ,xshift=-1.5cm ] {$ \text{Firm A} $};
					
					\node (end2) [startstop1,right of = CH ,yshift=0cm,xshift=1.5cm] {$ \text{Firm B} $};
					
					\node (sur) [startstop2 ,below of = end ,yshift=0cm,xshift=0cm] {$ \text{Firm X} $};
					
					\node (sur2) [startstop2,below of = end2 ,yshift=0cm,xshift=0cm] {$ \text{Firm Y} $};
					
					
					\draw [arrow] (end) --(sur);
					\draw [arrow] (end2) -- (sur2);
					
					
					\draw [arrow] (CH) -- (sur);
					\draw [arrow] (CH) -- (sur2);
					
					\draw [latex'-latex'] (sur) to [bend right =0]  node[sloped, anchor=center, below] {} (sur2);
					
					
				\end{tikzpicture}
			}   
			\hfill
			\resizebox{0.49\textwidth}{!}{
				\begin{tikzpicture}[node distance=2cm]
					
					
					\node (start) [startstop] { $ \text{Ultimate Owner} $};
					
					
					\node (CH) [process, below of = start,xshift=3.5cm] {Common Owner};
					
					\node (end) [startstop1,below of = start ] {$ \text{Firm A} $};
					
					\node (end2) [startstop1,right of = CH ,yshift=0cm,xshift=1.5cm] {$ \text{Firm B} $};
					
					\node (sur) [startstop2 ,below of = end ,yshift=0cm,xshift=0cm] {$ \text{Firm X} $};
					
					\node (sur2) [startstop2,below of = end2 ,yshift=0cm,xshift=0cm] {$ \text{Firm Y} $};
					
					
					
					\draw [arrow] (start) --(end);
					
					\draw [arrow] (end) --(sur);
					\draw [arrow] (end2) -- (sur2);
					
					\draw [dash dot,->] (start) -- (CH);
					
					\draw [arrow] (CH) -- (sur);
					\draw [arrow] (CH) -- (sur2);
					
					\draw [latex'-latex'] (sur) to [bend right =0]  node[sloped, anchor=center, below] {} (sur2);
					
					
				\end{tikzpicture}
			}
			\caption{ Pair not in the business group}
		\end{subfigure}
		\bigskip
		\bigskip
		\begin{subfigure}[t]{.49\linewidth}
			\centering
			\tiny
			\resizebox{1\textwidth}{!}{
				
				\begin{tikzpicture}[node distance=2cm]
					
					
					\node (start) [startstop] { \normalsize$ \text{Ultimate Owner A} $};
					\node (start2) [startstop,right of = start,xshift=5cm] {\normalsize$ \text{Ultimate Owner B} $};
					
					
					\node (CH) [process, below of = start2,xshift=-3.5cm] {\normalsize Common Owner};
					
					\node (end) [startstop1,below of = start ] {\normalsize $ \text{Firm A} $};
					
					\node (end2) [startstop1,below of = start2 ,yshift=0cm,xshift=0cm] {\normalsize $ \text{Firm B} $};
					
					\node (sur) [startstop2 ,below of = end ,yshift=0cm,xshift=0cm] {\normalsize $ \text{Firm X} $};
					
					\node (sur2) [startstop2,below of = end2 ,yshift=0cm,xshift=0cm] {\normalsize $ \text{Firm Y} $};
					
					
					
					\draw [arrow] (start) --(end);
					\draw [arrow] (start2) -- (end2);
					
					\draw [arrow] (end) --(sur);
					\draw [arrow] (end2) -- (sur2);
					
					\draw [dash dot,->] (start) -- (CH);
					\draw [dash dot,->] (start2) -- (CH);
					
					\draw [arrow] (CH) -- (sur);
					\draw [arrow] (CH) -- (sur2);
					
					\draw [latex'-latex'] (sur) to [bend right =0]  node[sloped, anchor=center, below] {} (sur2);
					
					
				\end{tikzpicture}
			}   
			\caption{ Pair in two distinct business group}
		\end{subfigure}
		\begin{subfigure}[t]{.49\linewidth}
			\centering
			\tiny
			\resizebox{1\textwidth}{!}{
				
				\begin{tikzpicture}[node distance=2cm]
					
					
					\node (start) [startstop] {\normalsize Ultimate Owner};
					
					
					
					\node (end) [startstop1,below of = start , yshift=0cm , xshift=-3.5cm ] {\normalsize $ \text{Firm A} $};
					\node (end2) [startstop1,below of = start , yshift=0cm , xshift=3.5cm ] {\normalsize $ \text{Firm B} $};
					
					
					
					\node (sur) [startstop2 ,below of = end ,yshift=0cm,xshift=0cm] {\normalsize $ \text{Firm X} $};
					
					
					\node (sur2) [startstop2 ,below of = end2 ,yshift=0cm,xshift=0cm] {\normalsize $ \text{Firm Y} $};
					
					
					\node (CH) [process, below of = start ,xshift=0] {\normalsize Common Owner};
					
					
					\draw [arrow] (start) --(end);
					\draw [arrow] (end) --(sur);
					
					\draw [arrow] (start) --(end2);
					
					\draw [arrow] (end) --(sur);
					\draw [arrow] (end2) -- (sur2);
					
					
					\draw [arrow] (CH) -- (sur);
					\draw [arrow] (CH) -- (sur2);
					\draw [dashed ,->] (start) --(CH);
					
					\draw [latex'-latex'] (sur) to [bend right =0]  node[sloped, anchor=center, below] {} (sur2);
					
					
				\end{tikzpicture}
			} 
			
			\caption{ Pair in the same business group}
		\end{subfigure}
		
		
		
	\end{figure}  
	
	
	\captionsetup[subfigure]{labelformat=empty}
	
\DeclareRobustCommand{\myname}{\input{Elements/pairsnumber.tex}}


	
				
		\captionsetup[subtable]{labelformat=parens}
			\renewcommand{\thesubtable}{\Alph{subtable}}
			 \begin{table}[htbp]
			 \caption{ Summary Statistics \\ \small
			 This table reports summary statistics of ownership features for all TSE stocks from 2014 to 2019. Panel \subref{t2-1} lists the total number of firms and Business groups and other features at the end of the fourth quarter of each year. Panel \subref{t2-2} reports the number of unique pairs in groups and outside for the fourth quarter of each year. The number of unique stock pairs is $ n(n-1)/2 $, where n is the number of stocks. We have \myname pairs in our sample.  }
			\label{st1}
			\centering
			\subcaption{ Ownership Characteristics for listed firms}
			\label{t2-1}
			\resizebox{1\textwidth}{!}
			{
				\input{Output/summaryOfOwnership.tex}
			}
			
		\centering
	\bigskip
			\subcaption{Number of Pairs, in, and outside the Business Groups }
		\label{t2-2}
		\resizebox{1\textwidth}{!}
		{
			\input{Output/summaryOfPairs.tex}
		}
	\end{table}
	
	\captionsetup[subtable]{labelformat=empty}

	
	
	


\FloatBarrier


\subsection{{Measurement of common-ownership}}


In table \ref{maasurmentsSummary} we summarize common ownership measurements which are used in literature. There are two groups of measurement for common ownership.
First of all, model-based measures that capture common ownership base on a proper  model. These measures have a better economic interpretation, but most of them are bi-directional or industry-level measures.(e.g, \cite{harford2011institutional}; \cite{azar2018anticompetitive}; \cite{gilje2020s})

In addition to model-based measures, some ad-hoc common ownership measures are used in the empirical literature. There is significant doubt on how these measures capture common ownership's impact on the management, and many of them have unappealing properties.(e.g, \cite{AntonPolk}; \cite{azar2011new}; \cite{freeman2019effects}; \cite{hansen1996externalities};  \cite{he2017product}; \cite{he2019internalizing}; \cite{lewellen2021does}; \cite{newham2018common})
	{\begin{table}[htbp]
			\centering
			\scriptsize
			\caption{ Common ownership measurements in the literature.}
			\label{maasurmentsSummary}
			\resizebox{\textwidth}{!}{
				\input{Elements/MeasurmentLit.tex}
			}
		\end{table}
	}
	
In our primary analysis, we estimate the impact of common ownership on pair's correlation. For this purpose, we need a pair-level measure with a good economic interpretation that is not bi-directional. As a result, we propose a modification for Anton's measure (\cite{AntonPolk}) that captures the extent of common ownership distribution and apply this measure in this study.

We reformulate mentioned Anton's measure in table \ref{maasurmentsSummary}. We re-weight this formula to capture the difference between ownership distribution ({For further discussion appendix \ref{ModifiedMeasure}}). Our proposed measure is
\begin{equation}
	\text{Overlap}_{Sqrt}(i, j) =  [\frac{\sum_{f =1}^{F}(\sqrt{S^f_{i,t}P_{i,t}}+\sqrt{S^f_{j,t}P_{j,t}})}{\sqrt{S_{i,t}P_{i,t}} + \sqrt{S_{j,t}P_{j,t}}}]^2 
	\label{sqrt}
\end{equation}
where $ S^f_{i,t}$ is the number of shares held by owner f at time t trading at price $ P{i,t} $ with total shares outstanding of $ S_{i,t} $, and similarly for stock j. Modified measure represent the number of equal percents held block-holder. In other words, If for a pair of stocks with n mutual owners, all owners have even shares of each firm's market cap, then the proposed index will be equal to number of holders.

On each day, we measure common ownership by our proposed measure and then report an average of these daily calculations for the entire period at the end of each month. We also calculate Anton's measure in this way. Panel \subref{measureResults} table \ref{st2} report snapshots of the distribution of common ownership measure for both methods. As we expected, the modified measure creates higher values for a high level of common ownership than Anton's measure. The average common ownership measure is five and three times larger, respectively, in business groups and industries.
%		\begin{table}[htbp]
%			%	\centering
%%			\toprule
%%			 & \multicolumn{5}{c}{MonthlyFCA} & \multicolumn{5}{c}{MonthlyFCAPf} \\
%%			 \cmidrule(lr){2-6} \cmidrule(lr){7-11}
%%			 &       mean &    std &    min & median &    max &         mean &    std &    min & median &    max \\
%%			\midrule
%			\caption{Calculation of common ownership with two measure}
%			\label{measureResults}
%			\resizebox{1\textwidth}{!}
%			{
%					{\input{Output/FCACal.tex}}
%			}
%		\end{table}
%		
%		\multirow{2}[3]{*}{variable} & \multicolumn{5}{c}{MFCAP} & \multicolumn{5}{c}{FCAP} \\
%		 \cmidrule(lr){2-6} \cmidrule(lr){7-11}
%		 &       mean &   std &   min & median &   max &         mean &   std &  min & median &   max \\
		
\FloatBarrier
\subsection{{Stock Return comovement}}
\label{comovement}

	We calculate the monthly correlation of each pair from stocks' daily abnormal returns. Benchmark for calculating abnormal return is the following equation which is a four-factor model plus industry return due to the importance of industries on stocks' return in the Tehran stock exchange (TSE) :
	\begin{equation}
		\begin{split}
			R_{i,t} =\alpha _{i}&+\beta _{mkt,i}{\mathit {R}}_{M,t} + \beta_{Ind,i}{\mathit {R}}_{Ind,t} + \\
			&+\beta _{HML,i}{\mathit {HML}}_{t}+\beta _{SMB,i}{\mathit {SMB}}_{t}+\beta _{UMD,i}{\mathit {UMD}}_{t}+ \varepsilon_{i,t}
		\end{split}
		\label{e5Factor}
	\end{equation}
	where $ R_{i,t} $, $ R_{M,t} $ and $ R_{Ind,t} $ are excess daily return of respectivly  firm, market and firm's industry from bank deposit's daily rate(risk free). Other variabales difinition is base on Carhart four-factor model [\cite{Carhart4Factor}].
	
	At the end of each month, we estimate our benchmark model base on the past three-month period (from two months before the end of the preceding month) and measure daily residuals.  After that, we calculate the monthly correlation of daily residuals during that month for the pair.
	
	We use other benchmarks (CAPM, 4 Factor, and Benchmark\footnote{we follow \cite{daniel1997measuring} to control risk characteristics: abnormal returns are calculated using a stock’s daily return minus the average return of
	the stock’s benchmark group, which is formed at every month’s end based on stocks’ capitalization and market-to-book ratio using the sample of all stocks}) for calculating a monthly correlation and report its summary in panel \subref{tCorr} table \ref{st2}. 
	As we expected,  models that include industry returns remove pairs' correlation. According to the results, it seems that our selected benchmark (4 Factor + Industry) almost captures all the pairs' comovement because it is nearly a zero mean variable. We use this correlation for our analysis but our results are robust for other models.
	
	
	
	
%{	\begin{table}[htbp]
%		\centering
%		\caption{\footnotesize This table reports distribution of calculated correlation base on different models.}
%		\label{tCorr}
%%		\resizebox{0.7\textwidth}{!}
%		{
%			\input{Output/CorrelationsResultsText.tex}
%		}
%	\end{table}}



\FloatBarrier


\subsection{Controls}

We are interested in the effects of common ownership and business group on pair's comovement.
Our prediction of a higher correlation for a connection dominates by stocks' intrinsic similarity, and these similarities motivate block-holders to hold these stocks simultaneously. These related stocks will comove regardless of who owns them.

The first group of controls is pair controls. These controls include
a dummy variable for whether two stocks are in the same industry, \textbf{SameIndustry}; a dummy variable for whether two stocks are in the same business group, \textbf{SameGroup}.
\input{Elements/sameindandsamebg}of pairs are in the same industry and business group. Furthermore, we control for cross-ownership between two stocks and define  \textbf{CrossOwnership} as the maximum percent of cross-ownership between two firms in the following month.


%	{\begin{table}[htbp]
%			\caption{\scriptsize This table reports the number of pairs in the same industry and business group.}
%			\label{SameGroupIndustry}
%			\centering 
%			{
%				\input{Output/SameGroupSameIndustry.tex}
%			}
%	\end{table}}


Another group of controls are firm-specific controls.  We define these variables base on  \cite{AntonPolk} methodology. One of these is size control based on the normalized rank-transform of the percentile market capitalization of the two stocks, \textbf{Size1} and \textbf{Size2} (where we label the
larger stock in the pair as the first stock). The other one is a book to market ratio based on the normalized rank-transform of the percentile book to market of the two stocks, \textbf{BM1} and \textbf{BM2}.
We also control these characteristics on a pair level. Our measures of similarity, \textbf{SameSize}, and \textbf{SameBM}, are the negative of the absolute difference in percentile ranking for a particular characteristic across a pair.


We calculate our controls daily and then report the average of these variables for the entire period at the end of each month. Panel \subref{ControlsSummary} table \ref{st2} shows the summary statistics of specified controls in this section. In addition


	\captionsetup[subtable]{labelformat=parens}
			\begin{table}[htbp]
			\caption{Summary Statistics of Pairs' Features\\ \small
			This table reports summary statistics for all the founded pairs from 2014 to 2019. Panel \subref{measureResults} reports snapshots from the calculation of common ownership for our measurement of common ownership (MFCAP) and \cite{AntonPolk} measure (FCAP). Panel \subref{tCorr} shows the distribution of calculated correlation of residuals for different models. Panel \subref{ControlsSummary} depicts Control variables' distribution.
			}
			\label{st2}
				%	\centering
%\toprule
%\multirow{2}{*}{Subset}& \multicolumn{5}{c}{MFCAP} & \multicolumn{5}{c}{FCAP} \\
%\cmidrule(lr){2-6} \cmidrule(lr){7-11}
%&       mean &    std &    min & median &    max &         mean &    std &    min & median &    max \\
%\midrule
				\subcaption{Common Ownership with for two measures}
				\label{measureResults}
				\resizebox{1\textwidth}{!}
				{
						{\input{Output/FCACal.tex}}
				}
				\bigskip
		\centering
		\subcaption{ Distribution of Correlation base on Different models}
		\label{tCorr}
%		\resizebox{1\textwidth}{!}
		{
			\input{Output/CorrelationsResultsText.tex}
		}
		
						\bigskip
					
 \subcaption{Distribution of specified Controls}
 \label{ControlsSummary}
               \centering 
%               	\resizebox{1\textwidth}{!}
                 {
    \input{Output/ControlsSummary.tex}
                 }
             \end{table}


\begin{table}[htbp]
\centerfloat
\caption{Summary Statistics of Sub-samples\\ \small
This table reports the mean of control variables for the three subsamples, for the pairs in the same business group, same industry, and high level of common ownership, which is in the fourth quarter of each period.}
\label{QarterSummary}
\resizebox{\textwidth}{!}{	
\input{"Output/table13.tex"}
}
\end{table}
	\captionsetup[subtable]{labelformat=empty}
